JuliaCon Proceedings in Quarto

### 2023-11-17 template.qmd
that's pretty close

>>>>

Alternatively, we can use the existing `lstlisting` environment for Julia code using the `julia` language option. This is the same environment that is used for Julia code in the existing LaTeX template. Under the hood, this uses a lua filter to convert the code to LaTeX. The code creates @fig-2 which can be cross-referenced as `@fig-2`.

```{julia}
#| label: fig-2
#| fig-cap: A figure caption.
#| eval: true
#| echo: true

x = -3.0:0.01:3.0
y = cumsum(rand(length(x)))
plot(x, y)
```

I don't know how to cross-reference the code itself.
